ODGI: understanding pangenome graphs

### 2022-02-10 manuscript/fig_extract_viz_draw_position_untangle.tex
explain what are MHC and C4, specifying the acronyms

        Visualizing the MHC and C4 pangenome graphs. \textbf{(a)} \textit{odgi draw} layout of the MHC pangenome graph extracted from a whole human pangenome graph of 90 haplotypes. The red rectangle highlights the C4 region.

>>>>

        Visualizing the \REVIEWED{major histocompatibility complex (MHC) and complement component 4 (C4)} pangenome graphs. \textbf{(a)} \textit{odgi draw} layout of the MHC pangenome graph extracted from a whole human pangenome graph of 90 haplotypes.
        \REVIEWED{The MHC locus is located on the human chromosome 6 and it encodes molecules involved in antigen presentation, inflammation regulation, the complement system, and the innate and adaptive immune responses~\citep{Shiina2009}.}
        The red rectangle highlights the C4 region\REVIEWED{, which encodes proteins involved in the complement system.}
